Bayesian exponential random graph modeling of KWL Burial network

### 2020-10-06 analysis/paper/paper.Rmd
Get first three moments of GOF distributions

We analyzed social networks using the R programming language with bergm package for Bayesian exponential random graph models [@Caimo2014], which built upon ergm package for simulation and model specification [@Hunter2008; @Morris2008; @Handcock2008]. Although exponential random graph models can describe a network by capturing the dependency structure, it is difficult to estimate model parameters and interpret the result due to the intractable normalizing constant and model degeneracy [@Caimo2014; @Jin2013]. A normalizing constant is an important step to make probability distribution to integrate to one, which becomes harder to compute with larger set of networks [@Caimo2017bayesian]. Degeneracy is another issue that probability models tend to overestimate a small number of extreme graphs by assigning too much weight, such as empty (all nodes unconnected) or complete graphs (all nodes connected) [@Schweinberger2011; @Caimo2014]. To overcome these limitations in ERGM, Bayesian model applies Markov chain Monte Carlo (MCMC) simulation with the approximate exchange algorithm to estimate the double intractable posteriors [@Caimo2011]. This alleviate above computational problems. By fitting an ERMG with MCMC algorithm, a Bayesian approach provides posterior probability that incorporates our sample data and prior information through summary statistics from estimates of the ERGM parameters. Posterior probability enables us to estimate the effect of ERGM parameter by observing the posterior mean and 95% credible intervals, which can replace p-value for accessing a null hypothesis [@Caimo2017bayesian]. The criteria is that the odds ratio grater than one means positive effect of ERGM parameter, while odds ratio less than one represents negative effect.

>>>>

We analyzed social networks using the R programming language with bergm package for Bayesian exponential random graph models [@Caimo2014], which built upon ergm package for simulation and model specification [@Hunter2008; @Morris2008; @Handcock2008]. Although exponential random graph models can describe a network by capturing the dependency structure, it is difficult to estimate model parameters and interpret the result due to the intractable normalizing constant and model degeneracy [@Caimo2014; @Jin2013]. A normalizing constant is an important step to make probability distribution to integrate to one, which becomes harder to compute with larger set of networks [@Caimo2017bayesian]. Degeneracy is another issue that probability models tend to overestimate a small number of extreme graphs by assigning too much weight, such as empty (all nodes unconnected) or complete graphs (all nodes connected) [@Schweinberger2011; @Caimo2014]. To overcome these limitations in ERGM, Bayesian model applies Markov chain Monte Carlo (MCMC) simulation using the approximate exchange algorithm to estimate the double intractable posteriors [@Caimo2011]. This alleviate above computational problems and gives a better convergence results. By fitting an ERMG with MCMC algorithm, a Bayesian approach provides posterior probability that incorporates our sample data and prior information through summary statistics from estimates of the ERGM parameters. Posterior probability enables the estimation the effect of ERGM parameter by looking at the posterior mean and 95% credible intervals, which can replace p-value for accessing a null hypothesis [@Caimo2017bayesian]. The criteria is that the odds ratio greater than one means positive effect of ERGM parameter, while odds ratio less than one represents negative effect.
